# fivemat: Better formatting for R

The **fivemat** package provides better formatting for R numbers. 
It has similar functionality to the base R functions `sprintf`, `prettyNum` and `formatC`, but with more features and support for locales.

This package is primarily a port  of the Javascript library [d3-format](https://github.com/d3/d3-format/blob/master/README.md).

# Installation

**fivemat** is not on CRAN, you can install the development version 
from github with
```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("jrnold/fivemat")
```

# Usage

The `fmt` function is the primary function in the package.
The formatting is defined using a mini-language similar to `sprintf`.
Some examples include:

A rounded percentage,
```{r}
fmt(c(0.1, 0.12, 0.123, 0.1234), ".0%")
fmt(c(0.1, 0.12, 0.123, 0.1234), ".1%")
```
a localized fixed-point currency,
```{r}
fmt(-3.5, "($.2f", locale = "en-GB")
fmt(-3.5, "($.2f", locale = "en-US")
```
a space-filled and signed number,
```{r}
fmt(42, "+20")
```
a dot-filled and centered number,
```{r}
fmt(42, ".^20")
```
SI-prefixed numbers with two significant digits,
```{r}
fmt(1.23 * 10 ^ seq(-24, 24, by = 1), ",.2s")
```
SI-prefixed numbers with one digit after the decimal point and
a common SI-prefix,
```{r}
fmt(1.23 * 10 ^ seq(-24, 24, by = 1), ".1", si = 1e3)
```
a prefixed lowercase hexadecimal number,
```{r}
fmt(48879, "#x")
```
a number grouped by thousands with two-significant digits,
```{r}
fmt(4223, ",.2r")
```

The `locale` argument supports localization of groupings, decimal marks, numerals,
```{r}
x <- 12345678910.12
fmt(x, "$,.2f", locale = "en-US")
fmt(x, "$,.2f", locale = "en-GB")
fmt(x, "$,.2f", locale = "en-IN")
fmt(x, "$,.2f", locale = "fr-FR")
fmt(x, "$,.2f", locale = "ar-SA")
fmt(x, "$,.2f", locale = "zh-CN")
fmt(x, "$,.2f", locale = "ja-JP")
```


The available default locales are in the `fmt_locales`.
The default locales are those provided by the [d3-format](https://github.com/d3/d3-format) Javascript library.

The `si` argument can be used to apply a common SI-prefix to all the values.
```{r}
fmt(c(0.00042, 0.0042), spec = ",.0", si = 1e-6)
```

Formats can be saved as a function to be reused,
```{r}
formatter <- fmt_new(",.2f")
formatter(c(1, 100, 1000, 1050, 1.50))
formatter(rnorm(5))
```
